Viscous Erosion in Porous Media

### 2018-03-11 docs/methods/erosion_methods.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Outline of the paper} In Section~\ref{s:formulation}, we
describe the governing equations for both the fluid and describe the
erosion model using a \thL~framework.  In Section~\ref{s:method}, the
numerical methods in both space and time are described.
Section~\ref{s:results} gives several numerical examples.  Finally,
concluding remarks are made in Section~\ref{s:conclusions}

@@

%%-----------------------------------------------------------------%%
% RESULTS SECTION
%%-----------------------------------------------------------------%%
\section{Results}
\label{s:results}
With the description of the methods complete, we now present numerical
results on bodies eroding in Stokes flow. We first discuss the case of a
single body, as certain features can be predicted analytically and thus
used for validation. We then discuss the erosion of multiple bodies and
highlight important differences that arise compared to the single-body
case.

@@

\subsection{Scaling law for the vanishing rate}
\label{sec:scaling}

@@

@@

\subsection{Multiple-body simulations}

@@

Briefly, to confirm that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed. The table shows the method to retain second-order accuracy in time. In the last column, we show the computational times, indicating that the 20-body simulations require more runtime than the single-body case. Although the GMRES-iteration count is independent of the spatial resolution, $N_{\iin}$, it can depend on the number of bodies and/or their configuration. To illustrate this point, we show in Table \ref{itertab} the GMRES count for various cases ...

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Outline of the paper} In Section~\ref{s:formulation}, we
describe the governing equations for both the fluid and describe the
erosion model using a \thL~framework.  In Section~\ref{s:method}, the
numerical methods in both space and time are described.
Section~\ref{SingleResults} gives several numerical examples.  Finally,
concluding remarks are made in Section~\ref{s:conclusions}

@@

%%-----------------------------------------------------------------%%
% RESULTS SECTION
%%-----------------------------------------------------------------%%
\section{Results: single-body erosion}
\label{SingleResults}
With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow. We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation. In Section \ref{MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.

@@

\subsection{Scaling laws for area and drag}
\label{sec:scaling}

@@

\subsection{Fixed-area simulations}

@@

\section{Results: multi-body erosion}
\label{MultiResults}

\subsection{Fixed pressure drop condition and validation}

@@

Briefly, to verity that the rescaling does not alter accuracy, we show in Table \ref{convtab} a convergence test for a 20-body simulation with the condition of fixed pressure drop imposed. The table confirms that the method retains second-order accuracy in time. In the last column, we show the computational times, indicating that the 20-body simulations require more runtime than the single-body case. Although the GMRES-iteration count is independent of the spatial resolution, $N_{\iin}$, it can depend on the number of bodies and/or their configuration. To illustrate this point, we show in Table \ref{itertab} the GMRES count for various cases ...

@@

\subsection{Multi-body erosion}
